---
title: "sbcfederalcontracts"
output: html_document
date: "2025-02-18"
---

load packages:

```{r}
library(tidyverse)
library(dbplyr)
library(tidyr)
library(lubridate)
library(ggplot2)
library(readr)

Assistance_PrimeAwardSummaries_2025_02_18_H12M03S23_1 <- read_csv("data/Assistance_PrimeAwardSummaries_2025-02-18_H12M03S23_1.csv")
Contracts_PrimeAwardSummaries_2025_02_18_H11M57S06_1 <- read_csv("data/Contracts_PrimeAwardSummaries_2025-02-18_H11M57S06_1.csv")
Contracts_Subawards_2025_02_18_H12M16S35_1 <- read_csv("data/Contracts_Subawards_2025-02-18_H12M16S35_1.csv")


```


load data:

```{r}
contractsubawards <- Contracts_Subawards_2025_02_18_H12M16S35_1
contractprimeawards <- Contracts_PrimeAwardSummaries_2025_02_18_H11M57S06_1
assistanceprimeawards <- Assistance_PrimeAwardSummaries_2025_02_18_H12M03S23_1
assistancesubawards <- Assistance_Subawards_2025_02_18_H12M44S33_1
```

which contracts are ongoing? which have ended? 

```{r}
contractsubawards %>%  filter(prime_award_period_of_performance_current_end_date >= '2025-01-01')
contractprimeawards %>%  filter(period_of_performance_current_end_date >= '2025-01-01')
assistanceprimeawards %>%  filter(period_of_performance_current_end_date >= '2025-01-01')
assistancesubawards %>%  filter(prime_award_period_of_performance_current_end_date >= '2025-01-01')
```


vet data:

is each instance unique?

```{r}
contractprimeawards %>%  count(contract_award_unique_key)
contractsubawards %>% count(prime_award_unique_key)
assistanceprimeawards %>% count(assistance_award_unique_key)
assistancesubawards %>% count(prime_award_unique_key)
```

what are all the t involved?

```{r}
contractprimeawards %>%  count(awarding_sub_agency_code) %>% 
  arrange(desc(n))

contractsubawards %>%  count(prime_award_awarding_sub_agency_code) %>% 
  arrange(desc(n))

assistanceprimeawards %>%  count(awarding_sub_agency_code) %>% 
  arrange(desc(n))

assistancesubawards %>%  count(prime_award_awarding_sub_agency_code) %>% 
  arrange(desc(n))
```

n sums out to 1319

What county are all of these from?

```{r}
contractprimeawards %>%  count(primary_place_of_performance_county_name)%>% 
  arrange(desc(n))

contractprimeawards %>%  count(primary_place_of_performance_city_name)%>% 
  arrange(desc(n))

contractsubawards %>%  count(prime_award_primary_place_of_performance_county_name)%>% 
  arrange(desc(n))

contractsubawards %>%  count(prime_award_primary_place_of_performance_city_name)%>% 
  arrange(desc(n))

assistanceprimeawards %>%  count(primary_place_of_performance_county_name)%>% 
  arrange(desc(n))

assistanceprimeawards %>%  count(primary_place_of_performance_city_name)%>% 
  arrange(desc(n))

assistancesubawards %>%  count(prime_award_primary_place_of_performance_county_name)%>% 
  arrange(desc(n))

assistanceprimeawards %>%  count(primary_place_of_performance_city_name)%>% 
  arrange(desc(n))

```
n is 1319 under primary place of performance county name
n sums to 1319 under primary place of performance city name

what years do the data represent?
```{r}
contractprimeawards %>%  count(award_base_action_date_fiscal_year) %>% 
  arrange(desc(n))
  
contractprimeawards %>%  count(award_latest_action_date_fiscal_year) %>% 
  arrange(desc(n))  

contractsubawards %>% count(prime_award_latest_action_date_fiscal_year) %>% 
  arrange(desc(n))

assistanceprimeawards %>%  count(award_latest_action_date_fiscal_year) %>% 
  arrange(desc(n))

assistancesubawards %>%  count(prime_award_latest_action_date_fiscal_year) %>% 
  arrange(desc(n))
```
Earliest year the data represents is 2003, latest is 2025
many contract stuff is very recent, same with assitance subawards  


Who is getting the money?
```{r}
contractprimeawards %>%  count(recipient_name) %>% 
  arrange(desc(n)) 
```

what kinds of awards are there?
```{r}
contractprimeawards %>%  count(award_type) %>% 
  arrange(desc(n)) 
```

```{r}
assistanceprimeawards %>% filter(awarding_sub_agency_code == "12D2")
assistancesubawards %>% filter(prime_award_awarding_sub_agency_code == "12F2")
assistancesubawards %>% filter(prime_award_awarding_sub_agency_code == "7590")
assistancesubawards %>% filter(prime_award_awarding_sub_agency_code == "6802")
assistancesubawards %>% count(subawardee_name) %>% 
  arrange(desc(n))

assistancesubawards[grep('75*', assistancesubawards$prime_award_awarding_sub_agency_code),]
```

```{r}

assistancesubawards %>% count(prime_award_cfda_numbers_and_titles) %>% 
  arrange(desc(n))

```

Grant programs to look at:
93.994: MATERNAL AND CHILD HEALTH SERVICES BLOCK GRANT TO THE STATES
93.568: LOW-INCOME HOME ENERGY ASSISTANCE	
10.215: SUSTAINABLE AGRICULTURE RESEARCH AND EDUCATION	

```{r}
assistancesubawards %>% filter(prime_award_cfda_numbers_and_titles == "93.994: MATERNAL AND CHILD HEALTH SERVICES BLOCK GRANT TO THE STATES")

assistancesubawards %>% filter(prime_award_cfda_numbers_and_titles == "93.568: LOW-INCOME HOME ENERGY ASSISTANCE")

assistancesubawards %>% filter(prime_award_cfda_numbers_and_titles == "10.215: SUSTAINABLE AGRICULTURE RESEARCH AND EDUCATION")
```

how much has been awarded?
```{r}
assistancesubawards %>% summarise(sum(prime_award_amount))
assistanceprimeawards %>% summarise(sum(total_funding_amount))
contractprimeawards %>%  summarise(sum(total_obligated_amount))
contractsubawards %>% summarise(sum(prime_award_amount, na.rm=T))
```
where is the money for current ongoing contracts going?

```{r}
assistancesubawards %>%  filter(prime_award_period_of_performance_current_end_date >= '2025-01-01') %>% 
  count(subawardee_name) %>% 
  arrange(desc(n))

assistancesubawards %>% count(prime_award_funding_agency_name) %>% 
  arrange(desc(n))

assistancesubawards %>%  filter(prime_award_period_of_performance_current_end_date >= '2025-01-01') %>% 
  count(prime_award_cfda_numbers_and_titles) %>% 
  arrange(desc(n))

assistancesubawards %>%  filter(prime_award_period_of_performance_current_end_date >= '2025-01-01') %>% 
  summarise(sum(prime_award_amount))

assistancesubawards %>%  filter(prime_award_period_of_performance_current_end_date >= '2025-01-01') %>% 
  summarise(sum(prime_award_amount))
```


```{r}
contractsubawards %>%  filter(prime_award_period_of_performance_current_end_date >= '2025-01-01') %>%
  count(subawardee_name) %>% 
  arrange(desc(n))

contractsubawards %>%  filter(prime_award_period_of_performance_current_end_date >= '2025-01-01') %>% 
  filter(subawardee_name == "PACIFIC SCIENTIFIC ENERGETIC MATERIALS COMPANY (CALIFORNIA LLC)")

contractsubawards %>%  filter(prime_award_period_of_performance_current_end_date >= '2025-01-01') %>%
  count(prime_awardee_parent_name) %>% 
  arrange(desc(n))

contractsubawards %>%  filter(prime_award_period_of_performance_current_end_date >= '2025-01-01') %>%
  count(prime_award_naics_description) %>% 
  arrange(desc(n))

contractsubawards %>%  filter(prime_award_period_of_performance_current_end_date >= '2025-01-01') %>%
  summarise(sum(prime_award_amount))

contractsubawards %>%  filter(prime_award_period_of_performance_current_end_date >= '2025-01-01') %>%
  count(prime_award_awarding_sub_agency_name) %>% 
  arrange(desc(n))
```
 
```{r}
contractprimeawards %>%  filter(period_of_performance_current_end_date >= '2025-01-01') %>% 
  count(recipient_name) %>% 
  arrange(desc(n))

contractprimeawards %>% filter(period_of_performance_current_end_date >= '2025-01-01') %>% 
  count(product_or_service_code_description) %>% 
  arrange(desc(n))

contractprimeawards %>%  filter(period_of_performance_current_end_date >= '2025-01-01') %>%
  count(funding_agency_name) %>% 
  arrange(desc(n))

```
 
```{r}
assistanceprimeawards %>%  filter(period_of_performance_current_end_date >= '2025-01-01') %>% 
  count(cfda_numbers_and_titles) %>% 
  arrange(desc(n))

assistanceprimeawards %>%  filter(period_of_performance_current_end_date >= '2025-01-01') %>% 
  count(recipient_name) %>% 
  arrange(desc(n))

assistanceprimeawards %>%  filter(period_of_performance_current_end_date >= '2025-01-01') %>% 
  count(awarding_agency_name) %>% 
  arrange(desc(n))

assistanceprimeawards %>% count(awarding_agency_name) %>% 
  arrange(desc(n))

assistanceprimeawards %>% filter(awarding_agency_name == "Department of Veterans Affairs")
```

What specifc grants do places in Hollister get?
```{r}
assistancesubawards %>% filter(prime_award_period_of_performance_current_end_date >= '2025-01-01') %>%
  filter(subawardee_name == "COUNTY OF SAN BENITO"|subawardee_name == "SAN BENITO, COUNTY OF")

assistancesubawards %>% filter(prime_award_period_of_performance_current_end_date >= '2025-01-01') %>%
  filter(subawardee_name == "HOLLISTER SCHOOL DISTRICT")

assistancesubawards %>% filter(prime_award_period_of_performance_current_end_date >= '2025-01-01') %>%
  filter(subawardee_name == "SAN BENITO HIGH SCHOOL DISTRICT")

assistancesubawards %>% filter(prime_award_period_of_performance_current_end_date >= '2025-01-01') %>%
  filter(subawardee_name == "AROMAS-SAN JUAN UNIF SCH DIST")

assistancesubawards %>% filter(prime_award_period_of_performance_current_end_date >= '2025-01-01') %>%
  filter(subawardee_name == "HOLLISTER, CITY OF")

assistancesubawards %>% filter(prime_award_period_of_performance_current_end_date >= '2025-01-01') %>% 
  filter(subawardee_name == "SAN BENITO COUNTY LOCAL TRANSPORTATION AUTHORITY")

assistancesubawards %>% filter(prime_award_period_of_performance_current_end_date >= '2025-01-01') %>% 
  filter(prime_award_awarding_agency_name == "Department of Transportation (DOT)")


```

plot when the current ending of these funds are 
```{r}
ongoingasssub <- assistancesubawards %>% filter(prime_award_period_of_performance_current_end_date >= '2025-01-01')

ongoingasssub %>%  count(prime_award_period_of_performance_current_end_date) %>% 
  arrange(desc(n))

ongoingconsub <- contractsubawards %>%  filter(prime_award_period_of_performance_current_end_date >= '2025-01-01')

ongoingassprime <- assistanceprimeawards %>%  filter(period_of_performance_current_end_date >= '2025-01-01')

ongoingconprime <- contractprimeawards %>%  filter(period_of_performance_current_end_date >= '2025-01-01')


ongoingasssub %>% ggplot(aes(x=prime_award_period_of_performance_current_end_date)) +
  geom_histogram()

ongoingconsub %>% ggplot(aes(x=prime_award_period_of_performance_current_end_date)) +
  geom_histogram()

ongoingassprime %>% ggplot(aes(x=period_of_performance_current_end_date)) +
  geom_histogram()

ongoingconprime %>% ggplot(aes(x=period_of_performance_current_end_date)) +
  geom_histogram()
```

what kinds of funds are ending on september 30 2025?

```{r}
ongoingasssub %>% filter(prime_award_period_of_performance_current_end_date == "2025-09-30")

ongoingasssub %>% filter(prime_award_period_of_performance_current_end_date == "2025-09-30") %>% 
  count(prime_award_base_transaction_description) %>% 
  arrange(desc(n))

ongoingasssub %>% filter(prime_award_period_of_performance_current_end_date == "2025-06-30")

ongoingasssub %>%  count(prime_award_base_transaction_description) %>% 
  arrange(desc(n))
```

most of the assistance subawards ending in june are vaccine funds for kids, most of the awards in august that are lapsing are education/child services-related

what infrastructure and development grants and contracts are ongoing in the county?

```{r}
 conprimeinfra <- contractprimeawards %>%  filter(period_of_performance_current_end_date >= '2025-01-01') %>%  
  filter(product_or_service_code_description == "ARCHITECT AND ENGINEERING- GENERAL: OTHER"|product_or_service_code_description == "ARCHITECT AND ENGINEERING- CONSTRUCTION: OTHER WAREHOUSE BUILDINGS"| product_or_service_code_description == "CONSTRUCTION OF OFFICE BUILDINGS"| product_or_service_code_description == "ENVIRONMENTAL SYSTEMS PROTECTION- ENVIRONMENTAL REMEDIATION"| product_or_service_code_description == "LEASE OR RENTAL OF EQUIPMENT- GROUND EFFECT VEHICLES, MOTOR VEHICLES, TRAILERS, AND CYCLES"| product_or_service_code_description == "SPECIAL STUDIES/ANALYSIS- GRAZING/RANGE"| product_or_service_code_description == "SUPPORT- PROFESSIONAL: ENGINEERING/TECHNICAL")

assprimeinfra <- assistanceprimeawards %>%  filter(period_of_performance_current_end_date >= '2025-01-01') %>%  
  filter(cfda_numbers_and_titles == "10.912: ENVIRONMENTAL QUALITY INCENTIVES PROGRAM"|cfda_numbers_and_titles == "10.427: RURAL RENTAL ASSISTANCE PAYMENTS"| cfda_numbers_and_titles == "10.924: CONSERVATION STEWARDSHIP PROGRAM"| cfda_numbers_and_titles == "10.924: CONSERVATION STEWARDSHIP PROGRAM"| cfda_numbers_and_titles == "10.868: RURAL ENERGY FOR AMERICA PROGRAM"| cfda_numbers_and_titles == "15.507: WATERSMART (SUSTAIN AND MANAGE AMERICA’S RESOURCES FOR TOMORROW)"| cfda_numbers_and_titles == "20.939: SAFE STREETS AND ROADS FOR ALL"| cfda_numbers_and_titles == "93.526: GRANTS FOR CAPITAL DEVELOPMENT IN HEALTH CENTERS; 93.526: FIP VERIFICATION")

consubinfra <- contractsubawards %>%  filter(prime_award_period_of_performance_current_end_date >= '2025-01-01') %>%  
  filter(prime_award_naics_description == "RESEARCH AND DEVELOPMENT IN THE PHYSICAL, ENGINEERING, AND LIFE SCIENCES (EXCEPT NANOTECHNOLOGY AND BIOTECHNOLOGY)"|prime_award_naics_description == "RESEARCH AND DEVELOPMENT IN THE PHYSICAL, ENGINEERING, AND LIFE SCIENCES (EXCEPT BIOTECHNOLOGY)"| prime_award_naics_description == "PROCESS, PHYSICAL DISTRIBUTION, AND LOGISTICS CONSULTING SERVICES"| prime_award_naics_description == "ALL OTHER MISCELLANEOUS GENERAL PURPOSE MACHINERY MANUFACTURING"| prime_award_naics_description == "ENGINEERING SERVICES")

asssubinfra <- assistancesubawards %>% filter(prime_award_period_of_performance_current_end_date >= '2025-01-01') %>%
  filter(prime_award_cfda_numbers_and_titles == "20.509: FORMULA GRANTS FOR RURAL AREAS AND TRIBAL TRANSIT PROGRAM"| prime_award_cfda_numbers_and_titles == "10.215: SUSTAINABLE AGRICULTURE RESEARCH AND EDUCATION"| prime_award_cfda_numbers_and_titles == "93.568: LOW-INCOME HOME ENERGY ASSISTANCE"|  prime_award_cfda_numbers_and_titles == "11.473: OFFICE FOR COASTAL MANAGEMENT"| prime_award_cfda_numbers_and_titles == "15.615: COOPERATIVE ENDANGERED SPECIES CONSERVATION FUND"| prime_award_cfda_numbers_and_titles == "20.513: ENHANCED MOBILITY OF SENIORS AND INDIVIDUALS WITH DISABILITIES"| prime_award_cfda_numbers_and_titles == "20.600: STATE AND COMMUNITY HIGHWAY SAFETY")
  
```

ira stuff

```{r}
iraiija <- assistanceprimeawards %>% filter(grepl("IRA|INFLATION", program_activities_funding_this_award)|(grepl("INFLATION", prime_award_base_transaction_description))| (grepl("INFRASTRUCTURE LAW", program_activities_funding_this_award)))

assistanceprimeawards %>% filter(period_of_performance_current_end_date >= '2025-01-01') %>% 
  filter(grepl("IRA|INFLATION", program_activities_funding_this_award)|(grepl("INFLATION", prime_award_base_transaction_description))| (grepl("INFRASTRUCTURE LAW", program_activities_funding_this_award)))

```

```{r}
assistanceprimeawards %>% filter(grepl("INFRASTRUCTURE LAW", program_activities_funding_this_award))

assistancesubawards %>% filter(grepl("IRA", prime_award_base_transaction_description))
```

```{r}
ongoingassprime %>% filter(period_of_performance_current_end_date == "2025-09-30")

ongoingasssub %>% filter(prime_award_period_of_performance_current_end_date == "2025-09-30") %>% 
  count(prime_award_base_transaction_description) %>% 
  arrange(desc(n))

ongoingassprime %>% count(period_of_performance_current_end_date) %>% 
  arrange(desc(n))

ongoingasssub %>%  count(prime_award_base_transaction_description) %>% 
  arrange(desc(n))

ongoingasssub %>%  filter(prime_award_base_transaction_description == "Title I Part A Basic Grants to LEAs")
```

```{r}

subawardsschools <- assistancesubawards %>% filter(prime_award_period_of_performance_current_end_date >= '2025-01-01') %>%
  filter(subawardee_name == "HOLLISTER SCHOOL DISTRICT"| subawardee_name == "SAN BENITO HIGH SCHOOL DISTRICT"| subawardee_name == "AROMAS-SAN JUAN UNIF SCH DIST"| subawardee_name == "NORTH COUNTY JOINT UNION SCHOOL DISTRICT"| subawardee_name == "SAN BENITO COUNTY OFFICE OF EDUCATION")

primeawardsschools <- assistanceprimeawards %>%  filter(period_of_performance_current_end_date >= '2025-01-01') %>% 
  filter(recipient_name == "CIENEGA UNION ELEMENTARY SCHOOL DISTRICT"| recipient_name == "JEFFERSON ELEMENTARY SCHOOL DISTRICT"| recipient_name == "PANOCHE ELEMENTARY SCHOOL DISTRICT"| recipient_name == "SOUTHSIDE ELEMENTARY SCHOOL DISTRICT"| recipient_name == "TRES PINOS UNION ELEMENTARY SCHOOL"| recipient_name == "WILLOW GROVE UNIFIED SCHOOL DISTRICT")


```


```{r}
subawardsschools %>% 
  count(prime_award_cfda_numbers_and_titles) %>% 
  arrange(desc(n))

subawardsschools %>% filter(prime_award_cfda_numbers_and_titles == "84.010: TITLE I GRANTS TO LOCAL EDUCATIONAL AGENCIES")

subawardsschools %>% filter(prime_award_cfda_numbers_and_titles == "84.367: SUPPORTING EFFECTIVE INSTRUCTION STATE GRANTS (FORMERLY IMPROVING TEACHER QUALITY STATE GRANTS)")

subawardsschools %>% filter(prime_award_cfda_numbers_and_titles == "84.365: ENGLISH LANGUAGE ACQUISITION STATE GRANTS")

subawardsschools %>% filter(prime_award_cfda_numbers_and_titles == "84.424: STUDENT SUPPORT AND ACADEMIC ENRICHMENT PROGRAM")

subawardsschools %>% filter(prime_award_cfda_numbers_and_titles == "10.555: NATIONAL SCHOOL LUNCH PROGRAM")

subawardsschools %>% filter(prime_award_cfda_numbers_and_titles == "10.558: CHILD AND ADULT CARE FOOD PROGRAM")

subawardsschools %>% filter(prime_award_cfda_numbers_and_titles == "84.048: CAREER AND TECHNICAL EDUCATION -- BASIC GRANTS TO STATES")


```

```{r}
subawardsschools %>% 
  group_by(subawardee_name) %>% 
  summarise(sum(subaward_amount)) 

primeawardsschools %>% group_by(recipient_name) %>% 
  arrange(desc(total_obligated_amount))
```

```{r}
sanbenitohigh <- assistancesubawards %>% filter(subawardee_name == "SAN BENITO HIGH SCHOOL DISTRICT")

aromasschd <- assistancesubawards %>% filter(subawardee_name == "AROMAS-SAN JUAN UNIF SCH DIST")

northcountysd <- assistancesubawards %>%  filter(subawardee_name == "NORTH COUNTY JOINT UNION SCHOOL DISTRICT")

hollistersd <- assistancesubawards %>%  filter(subawardee_name == "HOLLISTER SCHOOL DISTRICT")

sbcofficeed <- assistancesubawards %>%  filter(subawardee_name == "SAN BENITO COUNTY OFFICE OF EDUCATION")

cienegasd <- assistanceprimeawards %>% filter(recipient_name == "CIENEGA UNION ELEMENTARY SCHOOL DISTRICT")

jeffersonsd <- assistanceprimeawards %>% filter(recipient_name == "JEFFERSON ELEMENTARY SCHOOL DISTRICT")

jeffersonsd <- assistanceprimeawards %>% filter(recipient_name == "JEFFERSON ELEMENTARY SCHOOL DISTRICT")
```

```{r}
subawardsschools %>% filter(subawardee_name == "HOLLISTER SCHOOL DISTRICT")

subawardsschools %>% filter(subawardee_name == "AROMAS-SAN JUAN UNIF SCH DIST")

assistancesubawards %>%  filter(subawardee_name== "SAN BENITO COUNTY OFFICE OF EDUCATION")

```

